### 2017-07-29 README.Rmd
use updated fig in readme

```{r eval=FALSE, echo=FALSE}
library(magick)
points <- image_read("06_images/points.jpeg")
image_write(image_trim(points), "06_images/points_trim.jpeg")
```

![](06_images/points_trim.jpeg)

>>>>

```{r eval=FALSE, echo=FALSE}
library(magick)
points <- image_read("06_images/20170526/points_newnames_20170530.jpeg")
image_write(image_trim(points), 
            "06_images/20170526/points_newnames_20170530_trim.jpeg")
```

![](06_images/20170526/points_newnames_20170530_trim.jpeg)
